### 2019-03-19 1_introduction.tex
read intro

Challenges in heterogeneous and extreme-scale parallel and distributed
computing have lead to the rise of a wide variety of new programming
models and runtime systems. However, efforts to understand the
performance behavior of these system have been limited. In many cases,
programming models are evaluated with weak and/or strong scaling of a
bespoke set of carefully hand-written applications, which make it
difficult to understand how the results generalize to other
applications, and impossible to compare across systems. Furthermore,
these are not limit studies, and thus do nothing to elucide the
boundaries of the performance envelops of the respective systems.

@@

A variety of runtime systems are able to make use of parallelism
internally for a variety of purposes, from analysis of tasks, to
scheduling or the orchestration of data movement and
synchronization. In order to mitigate unwanted influence due to
unreasonable allocation of resources to such internal uses, METG
concerns \emph{effective} task execution, where the overall
computational efficiency meets some threshold (say, 50\%). If the
METG(50\%) of an application is, say, 1~ms, then this indicates that
the application can be executed with tasks as small as 1~ms while
maintaining at least 50\% overall efficiency.

>>>>

Challenges in heterogeneous and extreme-scale parallel and distributed
computing have lead to the rise of a wide variety of new programming
models and runtime systems. However, efforts to understand the
performance behavior of these systems have been limited. In many cases,
programming models are evaluated with weak and/or strong scaling of a
bespoke set of carefully hand-written applications, which make it
difficult to understand how the results generalize to other
applications, and impossible to compare across systems. Furthermore,
these are not limit studies, and thus do nothing to elucidate the
boundaries of the performance envelops of the respective systems.

@@

A variety of runtime systems are able to make use of parallelism
internally for a variety of purposes, from analysis of tasks, to
scheduling or the orchestration of data movement and
synchronization. In order to mitigate unwanted influence due to
unreasonable allocation of resources to such internal uses, METG
concerns \emph{effective} task execution, where the overall
computational efficiency meets some threshold (say, 50\%). If the
METG(50\%) of an application is, say, 1~ms, then this indicates that
the application can be executed with tasks as small as 1~ms while
maintaining at least 50\% overall efficiency. 
\textcolor{red}{TODO:explain what does efficiency mean here?}
